My title

### 2024-11-29 paper/paper.qmd
fixed citations

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (CITATION). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on a book's rating. The insight from this research not only clarify the key elements that make high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature and writing choices."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)
library(dplyr)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(scales)

@@

For generations, children's books have been a catalyst in children's development. Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness (CITATION). Given these significant developmental benefits, it can be said that the quality of the children's book matters greatly; choosing a well-written book can affect how it nurtures the next generation of mature, emotionally resilient individuals. This is why book rating systems hold significant importance; allowing readers to rate books on a scale from 0-5 (most commonly used scale) helps parents and educators assess whether a book is worth giving to children.

@@

In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION). First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2). Then, a logistic regression model was created to predict the probability of the book being "highly-rated", based on the chosen book characteristic variables.

The logistic regression model showed that ___ .The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.

This research paper is structured as follows: (SECTION 2) contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis. (SECTION 3) describes and justifies the logistic regression model that was produced in this report. (SECTION 4) highlights the result of the model, (SECTION 5) discusses some of the outcomes, weaknesses, and (SECTION APPENDIX) contains additional information on model details.

@@

The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics. It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed. For examples, children's books may have variations in ratings across countries. Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION).

@@

The dataset used in this paper was obtained from COOKSON (CITATION), who sourced it from Goodreads (CITATION). Cookson's dataset contained over 9,000 records of children's books that contained information of books such as title, author, ratings, publisher and more. In the initial step, data-cleaning was performed and relevant variables were selected. First, entries with missing information were filtered out, and variables that were irrelevant to this study were also removed, which included variables such as book title. Then, a new variable called "highly-rated" was created, which was a binary variable indicating if the book had a rating over 4 (1 if it exceeded 4, 0 else). After cleaning and creating this new variable, there were 9240 entries in the cleaned dataset.

Data analysis is performed using statistical programming language , along with packages ___

@@

```{r}
#| label: cleaned_dataset-preview
#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
#| message: false
#| echo: false
#| warning: false

@@

Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, which contains information on Children's book.

@@

Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high rated" had more pages on average than low-rated books. Furthermore, high rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively. High-rated books also received far more ratings on average at 8000 ratings, more than four times of low-rated books at an average of 2000 reviews per book. Lastly, Kindle covers had the highest proportion of "high-rated" books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in (CITE HERE)

```{r}
#| label: summary_statistic_dataset
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false
summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE),
    highest_proportion_cover = data %>%
      group_by(cover) %>%
      summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
      slice_max(high_rated_pct, n = 1) %>%
      pull(cover)
  )

@@

(CITATION HERE PICTURE ABOVE) shows the proportion of "highly-rated" books for each cover type. `Kindle Edition` books had the highest proportions of highly-rated books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively. This illustrates that generally, digitally formatted books had higher proportions of "highly-rated" books compared to physical formats. This finding also reflects the result from (TABLE)

@@

(CTATION HERE) shows that "high-rated" books have more page count than low-rated books. Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.

@@

data2 <- data %>% filter(rating >= 4)
data3 <- data %>% filter(rating < 4)
data2 <- data2 %>% mutate(group = "High Rated Books (>= 4)")
data3 <- data3 %>% mutate(group = "Low Rated Books (> 4)")

# Combine the two datasets
combined_data <- bind_rows(data2, data3)

avg_publish_years <- combined_data %>%
  group_by(group) %>%
  summarise(avg_publish_year = mean(publish_year, na.rm = TRUE))

# Create a combined scatter plot with facets
ggplot(combined_data, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal() +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
             color = "red", linetype = "dashed", size = 1) 
```
(CITATION) shows the relationship between a book's rating and the publish year. The horizontal axis shows the publish year, and vertical axis shows the rating of the book. The graph is split into two vertically, the top plot showing ratings of "high-rated" books and low-rated books. Low-rated books showed a higher concentration of publish year towards the right, suggesting a higher average publish year. By looking at the red line of fit (average publish year), "high-rated" books tend to be published before low-rated books.

@@

(FIGURE 5) shows the relationship between the rating of a book and the number of ratings it received. The red line indicates the cut-off for a book to be considered "highly-rated". It is apparent that books that are considered "highly_rated" (right of the red line) have far more ratings on average than low-rated books.

@@

This study employed a Bayesian logistic regression model to analyze the relationship between Children's book's "highly-rated" status and the characteristic of the book. The model is as follows:

@@

The rstanarm package (CITATION) was used in order to run the regression model mentioned above. The default priors of the rstanarm package was used (CITATION). These default priors are designed to be weakly informative, meaning they provide enough information to regularize the model and prevent extreme estimates, while being flexible to let the data drive the inference. By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations (Equation LIST).

@@

The predictor variables shown in (LIST HERE) were chosen due to the number of studies regarding their influence on ratings of books.

More specifically, I expect that

@@

After running the regression based on the model shown above, we get the coefficient values showcased in Table X (CITE HERE).

COEFFICIENT RANGE (CITE) represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0. In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being "highly-rated" when positive and "low-rated" when negative.

With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being "highly-rated", assuming all else held constant, reflecting the analysis that was seen in DATA (CITE HERE). In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a book being "highly-rated".

Although the publish year was not statistically significant according to the GRAPH (CITE), it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings (CITE) that "high-rated" books tend to have earlier publication years compared to "low-rated" ones.

```{r}
#| label: summary_statistic_cleaned_dataset3
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

As shown by SECTIOM  (RESULTS), the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated. In particular, these factors are likely independent of how readers perceive its quality or enjoyment. Short books can be impactful and concise, whereas longer books can offer richer detail.

Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions (CITATION). Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.

@@

The results in SECTION (RESULTS), indicated a big positive relationship between book cover types and its "highly-rated" status. In particular, the "Kindle Edition" book cover had the highest coefficient (NUMBER HERE). A potential explanation could be that ebooks (such as Kindle Edition) are often preferred over physical books for their convenience, affordability and accessibility. Additionally ebooks are often cheaper due to saving material costs and saving physical space. In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books (CITATION HERE). Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its big relationship compared to any other book cover types.

@@

While the result in SECTION (RESULT) showed that the publish year was statistically insignificant, (GRAPH) a small negative correlation which was expected. In particular, high-rated books had an older publish year than lowly-rated books.

@@

We used a posterior predictive check in FIGURE (CITE) to evaluate how well the model fits the data. This compares the observed data Y (CHANGE) against the replicated data y-REP (CHANGE) which was generated by our model in SECTION 3 (CITE). The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.

```{r}
#| label: summary_statistic_cleaned_dataset4
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

In FIGURE BELOW (CITE) we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER). Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "highly-rated" book.

```{r}
#| label: summary_statistic_cleaned_dataset5
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

@@

```{r}
#| label: summary_statistic_cleaned_dataset6
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3

@@

FIGURE X AND Y are the trace plot of the model and Rhat plot of the model respectively.

The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model.

Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 (CITE ALENXANDER)

```{r}
#| label: summary_statistic_cleaned_dataset7
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

plot(model_file, "rhat")

@@

```{r}
#| label: summary_statistic_cleaned_dataset72
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

modelplot(model_file, conf_level = 0.9, coef_omit = c(5,8)) +
  labs(x= "90% percent credibility interval")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (CITATION). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on a book's rating. The insight from this research not only clarify the key elements that make high rated childrens' book so high-rated, but also enhance future authors to push the boundaries of their literature and writing choices."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(arrow)
library(readr)
library(rstanarm)
library(modelsummary)
library(dplyr)
library(here)
library(ggplot2)
library(knitr)
library(scales)

@@

For generations, children's books have been a catalyst in children's development. Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness [@citeliterature]. Given these significant developmental benefits, it can be said that the quality of the children's book matters greatly; choosing a well-written book can affect how it nurtures the next generation of mature, emotionally resilient individuals. This is why book rating systems hold significant importance; allowing readers to rate books on a scale from 0-5 (most commonly used scale) helps parents and educators assess whether a book is worth giving to children.

@@

In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data [@citedata]. First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in @sec-data. Then, a logistic regression model was created to predict the probability of the book being high-rated, based on the chosen book characteristic variables.

The logistic regression model showed that book covers had the biggest influence on the likelihood of the book being high-rated, notably, the `Kindle Edition` type. The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.

This research paper is structured as follows: @sec-data contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis. @sec-model describes and justifies the logistic regression model that was produced in this report. @sec-result highlights the result of the model, @sec-discussion discusses some of the outcomes, weaknesses, and @sec-appendix contains additional information on model details.

@@

The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics. It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed. For examples, children's books may have variations in ratings across countries. Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@sec-data].

@@

The dataset used in this paper was obtained from Cookson [@citedata]. Cookson's dataset contained over 9,000 records of children's books that contained information of books such as title, author, ratings, publisher and more. In the initial step, data-cleaning was performed and relevant variables were selected. First, entries with missing information were filtered out, and variables that were irrelevant to this study were also removed, which included variables such as book title. Then, a new variable called "highly-rated" was created, which was a binary variable indicating if the book had a rating over 4 (1 if it exceeded 4, 0 else). After cleaning and creating this new variable, there were 9240 entries in the cleaned dataset.

Data analysis is performed using statistical programming language , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].

@@

```{r}
#| label: tbl-cleaned-dataset-preview
#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
#| message: false
#| echo: false
#| warning: false

@@

@tbl-cleaned-dataset-preview presents the first 5 rows from the cleaned dataset, which contains information on children's book.

@@

@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered high-rated had more pages on average than low-rated books. Furthermore, high-rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively. High-rated books also received far more ratings on average at 8000 ratings, more than four times of low-rated books at an average of 2000 reviews per book. Lastly, Kindle covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in @sec-data.

```{r}
#| label: tbl-summary-statistic
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false
summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE),
    highest_proportion_cover = data %>%
      group_by(cover) %>%
      summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
      slice_max(high_rated_pct, n = 1) %>%
      pull(cover)
  )

@@

@fig-most-common-covers shows the proportion of `high-rated` books for each cover type. `Kindle Edition` books had the highest proportions of `high-rated` books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively. This illustrates that generally, digitally formatted books had higher proportions of `high-rated` books compared to physical formats. This finding also reflects the result from @tbl-summary-statistic.

@@

@fig-page-count shows that `high-rated` books have more page count than low-rated books. Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.

@@

#removing NA values
data_combined <- data %>%
  filter(!is.na(rated_high), !is.na(publish_year), publish_year >= 1980) %>%
  mutate(
    rating_category = ifelse(rated_high == 1, "High-Rated", "Not High-Rated")
  )

# Create

# Create a data frame for vertical lines
vertical_lines <- data.frame(
  rating_category = c("High-Rated", "Not High-Rated"),  # Match facet categories
  line_year = c(2003, 2005)  # Years for vertical lines
)

# Create the faceted bar plot with vertical lines
ggplot(data_combined, aes(x = as.factor(publish_year))) +
  geom_bar(fill = "steelblue") +
  geom_vline(
    data = vertical_lines,
    aes(xintercept = line_year),
    color = "red",
    linetype = "dashed",
    size = 1,
    inherit.aes = FALSE
  ) +
  labs(
    title = "Number of Books by Publish Year and Rating Category",
    x = "Publish Year",
    y = "Number of Books"
  ) +
  facet_wrap(~rating_category, ncol = 1) +  # Facet by rating category
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1)  # Tilt x-axis labels
  )

@fig-publish-year shows the relationship between a book's rating and the publish year. The horizontal axis shows the publish year, and vertical axis shows the rating of the book. The graph is split into two vertically, the top plot showing ratings of high-rated books and low-rated books. It showed a left-tail distribution, peaking around the mid 2010s, followed by a big drop in late 2010s. High-rated books had a lower average publish year than low-rated books, at 2003 and 2005 respectively.

@@

@fig-rating-count shows the relationship between the rating of a book and the number of ratings it received. The red line indicates the cut-off for a book to be considered high-rated. It is apparent that books that are considered high_rated (right of the red line) have far more ratings on average than low-rated books.

@@

This study employed a Bayesian logistic regression model to analyze the relationship between children book's `high-rated` status and the characteristic of the book. The model is as follows:

@@

The rstanarm package [@citerstanarm] was used in order to run the regression model mentioned above. The default priors of the rstanarm package was used [@citerstanarm]. These default priors are designed to be weakly informative, meaning they provide enough information to regularize the model and prevent extreme estimates, while being flexible to let the data drive the inference. By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations \ref{eq3}, \ref{eq4}, \ref{eq5}, \ref{eq6}, \ref{eq7}, \ref{eq8}, \ref{eq9}, \ref{eq10}, \ref{eq11}.

@@

The Bayesian logistic regression model was chosen because it is well-suited for binary outcome variables, making it appropriate for analyzing the likelihood of books being high-rated. Additionally, Bayesian methods enables the incorporation of prior knowledge and uncertainty into the analysis, which provides more robust estimates of the model parameters. [@citehannah]

@@

After running the regression based on the model shown above, we get the coefficient values showcased in @tbl-book-model.

@fig-interval represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0. In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being high-rated when positive and low-rated when negative.

With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being `high-rated`, assuming all else held constant, reflecting the analysis that was seen in @sec-data. In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a the likelihood of a book being high-rated.

Although the publish year was not statistically significant according to the @fig-interval, it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings @fig-publish-year that `high-rated` books tend to have earlier publication years compared to low-rated ones.

```{r}
#| label: tbl-book-model
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false

@@

As shown by @sec-result, the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated. In particular, these factors are likely independent of how readers perceive its quality or enjoyment. Short books can be impactful and concise, whereas longer books can offer richer detail.

Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions [@citeherd]. Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.

@@

The results in @sec-result, indicated a big positive relationship between book cover types and its high-rated status. In particular, the "Kindle Edition" book cover had the highest coefficient (4.239). A potential explanation could be that ebooks (such as Kindle Edition) are often preferred over physical books for their convenience, affordability and accessibility. Additionally ebooks are often cheaper due to saving material costs and saving physical space. In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books [@citepreference]. Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its big relationship compared to any other book cover types.

@@

While the result in @sec-result showed that the publish year was statistically insignificant, @fig-publish-year showed a small negative correlation. In particular, high-rated books had an older publish year than lowly-rated books.

@@

We used a posterior predictive check in @fig-distribution to evaluate how well the model fits the data. This compares the observed data `y` against the replicated data \mbox{y$_i$} which was generated by our model in @sec-model. The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.

```{r}
#| label: fig-distribution
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false

@@

In @fig-post-prior we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER). Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "highly-rated" book.

```{r}
#| label: fig-post-prior
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false
#| 
analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
model_file <- readRDS(file = here::here("models/model.rds"))

@@

```{r}
#| label: fig-trace
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3
#| warning: false
#| 
model_file <- readRDS(file = here::here("models/model.rds"))

@@

@fig-trace and @fig-rhat are the trace plot of the model and Rhat plot of the model respectively. The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model. Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 (CITE ALENXANDER)

```{r}
#| label: fig-rhat
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false

model_file <- readRDS(file = here::here("models/model.rds"))
plot(model_file, "rhat")

@@

```{r}
#| label: fig-interval
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false

model_file <- readRDS(file = here::here("models/model.rds"))
modelplot(model_file, conf_level = 0.9, coef_omit = c(5,8)) +
  labs(x= "90% percent credibility interval")
```
